An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-10-31 algorithmRjournal/kobakian_sugarbag.Rmd
New name

---
title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    email:  stephanie.kobakian@monash.edu
  - name: Dianne Cook
    affiliation: Monash University
    email:  dicook@monash.edu
bibliography: RJreferences.bib
link-citations: true
fig_caption: yes
abstract: >
  This algorithm creates a hexagon to represent each of the spatial polygons provided. It allocates these hexagon in a manner that preserves the spatial relationship of the areas. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on large geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

Choropleths are the current best practice approach for presenting geographical data as
maps highlight the geographic patterns in geospatially related statistics [@SAMGIS].
The land on the map space is divided to separate each area, these boundaries are usually administrative. The areas are filled with colour to represent the value of the statistic for the area [@EI].

<!-- urbanisation -->
In Australia, government bodies such as the Australian Bureau of Statistics, or the Australian Electoral Commission hold the responsibility for the division of areas. These boundaries are often adjusted as the population in areas increase. Australian people are increasingly congregating around major cities, the rural areas are often sparsely populated in comparison to the urban centres. 
The division of the population into equal population areas results in dramatically different square meterage of the geographic areas. 
This results in an unequal presentation of the statistic in each area, this can misrepresent the spatial distributions of the human related statistics in geographic maps.

<!-- solutions -->
Beginning with the geography, cartograms apply a transformation to place importance on the statistic of interest. They result in a distortion of the map space to represent differences in the statistic. 
These displays rely on the statistic of interest to determine the layout, however for Australia, many cartograms fail to preserve a recognisable display.
Contiguous cartograms change the shape of an area, preserving neighbouring relationships. Non-contiguous cartograms maintain the shape of each area, but lose the connection to neighbours.

Alternative maps shift the focus from land area, to the value of the statistics in a group of areas.
Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.

Tilegrams are an extension of Dorling cartograms, using one simple shape to represnt each area. This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area. These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.

@@

 1. Create the set of centroids to allocate
 2. Create the set of hexagons to use
 3. Allocate each centroid to an available hexagon
 4. Transform the data for plotting

@@

The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the \CRANpkg{sf} set of shapes used. If users already have a grid and set of centroids they may choose to only use the `allocate` function.

@@

The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
A single column of the data set must be used to identify the unique areas. 
In this case, the unique LGA codes associated with each LGA have been used.

@@

When utilising individual `sugarbag` functions, we recommend the following approach:
Begin with a set of polygons. The set should be provided as an `sf` object, this is a data frame containing a `geometry` column. ^[The `read_shape` function can assist in creating this object.] We will use the Local Government Areas of Tasmania, downloaded from the Australian Bureau of Statistics.

The centroids can be derived from the set of polygons:
```{r cents, message=FALSE, warning=FALSE, comment = FALSE}
centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
```
```{r derive_centroids, echo = FALSE}
## Use the create_centroids function to find polygon centroids:
## Join to data for each area
centroids <- left_join(centroids,
  sf::st_drop_geometry(tas_lga), by = "LGA_CODE16")
```

```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5, echo = FALSE}
fort_lga <- fortify_sfc(tas_lga)
polys <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") +theme_void() + coord_equal()

cents <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()

@@

A tilegram allows areas to be allocated to a tellesated set of tiles.
The grid is created to ensure a close point is found, that ensures tessellation with other previously allocated points.

@@

hex_size = 0.3

@@

### Step 1: Expand the grid

A sequence is created for longitude columns, and another for latitude rows.
The sequences begin at the minimum longitude (latitude), minus the buffer distance.
Equally spaced intervals the size of the hexagons are created up to the maximum longitude (latitude), plus the buffer distance.
An individual point is created from all intersections of the longitude columns and latitude row sequences.
```{r grid, echo = FALSE}
grid <- tibble::as_tibble(
  expand.grid(
    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
      bbox$max[1] + buffer_dist, # maximum
      hex_size), # distance between hexagons
    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
      bbox$max[2] + buffer_dist, # maximum
      hex_size))) # distance between hexagons

grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
```
A square grid will not facilitate tessellated hexagons. Every second latitude row of points will be shifted right by half of the hexagon size.
```{r shift, echo = FALSE}
# Find every second latitude
shift_lat <- grid %>% dplyr::select(hex_lat) %>%
    dplyr::distinct() %>%
    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()

@@

grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)

@@

@@

ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
```

@@

```{r split_centroids, echo = FALSE}
# Split the centroid data set
centroids <- centroids %>% 
  nest(longitude, latitude) %>% 
  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
  unnest(data, closest) %>% 
  arrange(focal_distance)
```

@@

```{r centroids, eval = FALSE, fig.height = 2.5, fig.width = 2.5}
hexmap_allocation <- allocate(
  centroids = centroids,
  sf_id = "LGA_CODE16",
  hex_grid = grid,
  hex_size = 0.2, # same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE
)
```

@@

```{r plot_buffer, echo = FALSE}
buff1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
```

@@

        f_angle <- centroid1 %>%
            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
                angle = (atan*180/pi),
                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()

@@

```{r plot_circle, echo = FALSE}
buff2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
```

@@

```{r buffer_slice, echo = FALSE}
# Filter for angle within circle

        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
            hex_grid <- hex_grid %>%
                # create slice of 60 degrees from centroid
                filter(angle_minus < hex_angle & hex_angle < angle_plus)
        } else {
            hex_grid <- hex_grid %>%
                # create slice of 60 degrees from centroid
                filter(hex_angle < angle_plus | angle_minus > hex_angle)
        }

buff3 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) 
```

@@

```{r allocated, echo = FALSE}
hex_points_df <- centroid_allocation %>% 
  fortify_hexagon(hex_size = hex_size,
  sf_id = "LGA_CODE16")

buff4 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
  geom_point(aes(x=longitude1, y = latitude1), data = centroid1, colour = "#fb9a99", size = 1) + 
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) + 
  theme_void() +
  coord_equal()
```

@@

```{r full_hexmapcode, echo = TRUE, warning = FALSE}
# Create centroids set
centroids <- create_centroids(tas_lga, "LGA_CODE16")
# Create hexagon location grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.3,
    buffer_dist = 1.2)
# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "LGA_CODE16",
  # same column used in create_centroids
  hex_size = 0.3,
  # same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE
)
```

@@

```{r create_plot_final, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
h1 <- hex_allocated %>%
  fortify_hexagon(hex_size = 0.3, 
  sf_id = "LGA_CODE16") %>% 
  left_join(., tas_lga)
```

```{r plot_final, echo = FALSE, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
p1 <- fortify_sfc(tas_lga)
end_hex <- ggplot() +
  geom_polygon(data = p1, aes(x=long, lat, group = interaction(LGA_NAME16, polygon)), fill = "grey", size = 0.3, colour = "lightgrey") +
  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()

>>>>

---
title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    email:  stephanie.kobakian@monash.edu
  - name: Dianne Cook
    affiliation: Monash University
    email:  dicook@monash.edu
bibliography: RJreferences.bib
link-citations: true
fig_caption: yes
abstract: >
  This algorithm creates a hexagon to represent each of the spatial polygons provided. It allocates these hexagon in a manner that preserves the spatial relationship of the areas. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on large geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
editor_options: 
  chunk_output_type: console
---

@@

Choropleths are current practice for presenting geographical data on a map, as they highlight the geographic patterns in geospatially related statistics [@SAMGIS].
The land on the map space is divided into separate areas, these boundaries are usually administrative, such as states or counties. The areas are filled with colour to represent the value of the statistic for the area [@EI].

<!-- urbanisation -->
Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
In Australia, government bodies such as the Australian Bureau of Statistics, and the Australian Electoral Commission hold the responsibility for the division of areas.
These boundaries are adjusted as the population increases. 
The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas. 
This results in an unequal visualisation of the statistic in each area, this can allow misrepresentation of the spatial distributions of human related statistics in geographic maps.

<!-- solutions -->
A solution to this visualisation problem begins with the geography. Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest. These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC]. 
These displays rely on the statistic of interest to determine the layout.
Australian population statistics often result in a cartogram that fails to preserve a recognisable display due to the difference in size of metropolitan and rural areas, a common feature of British Colonies [@ACTUC].
Contiguous cartograms change the shape of an area, preserving neighbouring relationships. Non-contiguous cartograms maintain the geographic shape of each area, but lose the connection to neighbours.
Population cartograms use either of these methods with population as the statistic of interest [@GOINO].

Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas.
Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different despite best efforts to normalise the areas using boundary shifts, but recognises that each area is equally important.

Tilegrams are an extension of Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC], using one simple shape to represnt each area. This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area. These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.

@@

 1. Create the set of centroids to allocate
 2. Create the grid of hexagons to use
 3. Allocate each centroid to an available hexagon
 4. Transform the data for plotting

@@

The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the simple features (\CRANpkg{sf}) set of shapes used. If users already have a grid and set of centroids they may choose to only use the `allocate` function.

@@

The polygon set of Local Government Areas (sa2) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_sa2`. 
A single column of the data set must be used to identify the unique areas. 
In this case, the unique sa2 codes associated with each sa2 have been used.

@@

When utilising individual `sugarbag` functions, we recommend the following approach:
Begin with a set of polygons. The set should be provided as an `sf` object, this is a data frame containing a `geometry` column. ^[The `read_shape` function can assist in creating this object.] We will use the Statistical Areas of Tasmania, at Level 2, downloaded from the Australian Bureau of Statistics.

The centroids can be derived from the set of polygons:
```{r cents, message=FALSE, warning=FALSE, comment = FALSE}
centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
```

```{r derive_centroids, echo = FALSE}
## Use the create_centroids function to find polygon centroids:
## Join to data for each area
centroids <- left_join(centroids,
  sf::st_drop_geometry(tas_sa2), by = "SA2_NAME16")
```

```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5, echo = FALSE}
fort_sa2 <- fortify_sfc(tas_sa2)

polys <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +theme_void() + coord_equal()

cents <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()

@@

A tilegram allocates areas to a tellesated set of tiles.
The grid is created to ensure tessellation with other previously allocated points.

@@

hex_size = 0.2

@@

### Step 1: Inital grid

Creating the grid involves using the centroids provided to find the minimum and maximum, longitude and latitude centroid values.
The buffer distance is used to extend the equally spaced rows and columns from the minimum longitude (latitude) minus the buffer distance, up to the maximum longitude (latitude) plus the buffer distance.
The set of longitude columns, and latitude rows  are created to define hexagons which are the size specified by `hex_size`.
An individual hexagon location is created from all intersections of the longitude columns and latitude rows.

```{r grid, echo = FALSE}
grid <- tibble::as_tibble(
  expand.grid(
    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
      bbox$max[1] + buffer_dist, # maximum
      hex_size), # distance between hexagons
    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
      bbox$max[2] + buffer_dist, # maximum
      hex_size))) # distance between hexagons

grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
```

A square grid will not facilitate tessellated hexagons. Every second latitude row of points must be shifted right by half of the hexagon size.

```{r shift, echo = FALSE}
# Find every second latitude
shift_lat <- grid %>% dplyr::select(hex_lat) %>%
    dplyr::distinct() %>%
    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()

@@

grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)

@@

```{r fort_grid, echo = FALSE}
fort_grid <- fortify_hexagon(data = grid, sf_id = "id", hex_size = 0.2)

@@

ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey")  +
  geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +
  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
```

@@

```{r split_centroids, echo = FALSE}
# Split the centroid data set
centroids <- centroids %>% 
  nest(data = c(longitude, latitude)) %>% 
  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
  unnest(c(data, closest)) %>% 
  arrange(focal_distance)
```

@@

```{r centroids, eval = FALSE, fig.height = 2.5, fig.width = 2.5}
hexmap_allocation <- allocate(
  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
  sf_id = "SA2_NAME16",
  hex_grid = grid,
  hex_size = 0.2, # same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE
)
```

@@

```{r plot_buffer, echo = FALSE}
buff1 <- ggplot()+
   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") + theme_void() +
    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
  theme_void() + coord_equal() 
```

@@

        f_angle <- centroid1 %>%
            mutate(atan = atan2(latitude-focal_latitude,longitude-focal_longitude),
                angle = (atan*180/pi),
                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()

@@

```{r plot_circle, echo = FALSE}
buff2 <- ggplot() + 
   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") + theme_void() +
    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
  theme_void() + coord_equal()

@@

```{r buffer_slice, echo = FALSE}

# Filter for angle within circle
  if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
     hex_grid <- hex_grid %>%
         # create slice of 60 degrees from centroid
         filter(angle_minus < hex_angle & hex_angle < angle_plus)
  } else {
     hex_grid <- hex_grid %>%
         # create slice of 60 degrees from centroid
         filter(hex_angle < angle_plus | angle_minus > hex_angle)
  }

buff3 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +  
   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
  geom_point(aes(x=focal_longitude, y = focal_latitude), data = centroid1, colour = "red") +
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") +
    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") + 
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
  theme_void() + coord_equal()

@@

```{r allocated, echo = FALSE}
hex_points_df <- centroid_allocation %>% 
  fortify_hexagon(hex_size = hex_size,
  sf_id = "SA2_NAME16")

buff4 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +  
    geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
  geom_point(aes(x=focal_longitude, y = focal_latitude), data = centroid1, colour = "red") +
  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") +
    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") + 
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
  theme_void() + coord_equal() 
```

@@

```{r full_hexmapcode, echo = TRUE, warning = FALSE}
# Create centroids set
centroids <- create_centroids(tas_sa2, "SA2_NAME16")
# Create hexagon location grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)
# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  # same column used in create_centroids
  hex_size = 0.2,
  # same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE
)
```

@@

```{r create_plot_final, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
h1 <- hex_allocated %>%
  fortify_hexagon(hex_size = 0.2, 
  sf_id = "SA2_NAME16") %>% 
  left_join(., tas_sa2)
```

```{r plot_final, echo = FALSE, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
p1 <- fortify_sfc(tas_sa2)
end_hex <- ggplot() +
  geom_polygon(data = p1, aes(x=long, lat, group = interaction(SA2_NAME16, polygon)), fill = "grey", size = 0.2, colour = "lightgrey") +
  geom_polygon(aes(x=long, y = lat, group = SA2_NAME16), data = h1, colour = "white", fill = "#b2df8a") + theme_void() + coord_equal()
